---
output: html_document
---

### Problem 4

*Chapter 5, Exercise 9 (Sec. 5.4, p. 201)*

```{r, echo=FALSE, warning=F}
library(MASS); library(boot); library(ggplot2)
```

```{r, warning=F}
m = Boston$medv
qplot(m, xlab = 'medv values')
```

#### Part A

```{r}
m.mean = mean(m)
m.mean
```

#### Part B

```{r}
m.std_err = sd(m)/sqrt(nrow(Boston))
m.std_err
```

This standard error is fairly low, though it could be better.

#### Part C


```{r}
# Inspiration for the following code comes from:
#   stats.stackexchange.com/questions/22472/use-of-standard-error-
#   of-bootstrap-distribution

m.bs = boot(m, function(d, i) mean(d[i]), 1000)

# The standard error from bootstrap is simply the standard deviation
# of the bootstrap distribution:
sd(m.bs$t)
```

The bootstrap method's standard error is very similar to that of part (b).

#### Part D

```{r}
boot.ci(m.bs, type='bca')
t.test(Boston$medv)
```

These result in nearly identical confidence intervals, with a difference of `< 0.1` on each end.

#### Part E

```{r}
m.median = median(m)
m.median
```

#### Part F

```{r}
m.bs = boot(m, function(d, i) median(d[i]), 1000)
sd(m.bs$t)
```

The standard error of the median using the bootstrap (`0.385`) is somewhat lower than that of the mean (`0.419`).

#### Part G

```{r}
u10 = quantile(m, c(.10))
```

#### Part H

```{r}
m.bs = boot(m, function(d, i) quantile(d[i], c(.10)), 1000)
sd(m.bs$t)
```

Our standard error increases significantly when we try to predict the 10th percentile. This is understandable; since our data basically takes the form of a normal distribution, the bulk of the data is in the middle, while there are far fewer examples to draw upon on the edges.